\documentclass[11pt]{article}

% ----------------- Packages -----------------%
\usepackage[margin=0.5in]{geometry}  % Adjust page margins
%\usepackage{hyperref}                % Clickable links
\usepackage{titlesec}                % Adjust spacing for sections
\usepackage{setspace}                % Control line spacing
\usepackage[T1]{fontenc} % font
\usepackage[hidelinks]{hyperref}   % hides links

% ----------------- Spacing Adjustments -----------------%
% Adjust line spacing here:
\linespread{0.8} % e.g., 1.0 = single space, 1.05 slightly more

% ----------------- Section Spacing Control -----------------%
% Common format for all section levels (numbered and unnumbered)
\titleformat{\section}{\normalfont\Large\bfseries}{}{0pt}{}
\titleformat{\subsection}{\normalfont\large\bfseries}{}{0pt}{}
\titleformat{\subsubsection}{\normalfont\normalsize\bfseries}{}{0pt}{}

% Base spacing values that you can easily adjust
\newcommand{\sectiontopspace}{0.7ex}
\newcommand{\sectionbottomspace}{0.7ex}

% Apply spacing to all section levels with proportional scaling
% Command, left indent, before skip, after skip
\titlespacing{\section}{0pt}{\sectiontopspace}{\sectionbottomspace}
\titlespacing{\subsection}{0pt}{0.8\sectiontopspace}{0.8\sectionbottomspace}
\titlespacing{\subsubsection}{0pt}{0.8\sectiontopspace}{0.8\sectionbottomspace}

% Unnumbered sections (starred versions) get the same treatment
\titlespacing{name=\section,numberless}{0pt}{\sectiontopspace}{\sectionbottomspace}
\titlespacing{name=\subsection,numberless}{0pt}{0.8\sectiontopspace}{0.8\sectionbottomspace}
\titlespacing{name=\subsubsection,numberless}{0pt}{0.8\sectiontopspace}{0.8\sectionbottomspace}

% Remove paragraph indentation, define paragraph spacing:
\setlength\parindent{0pt}  % No paragraph indent
\setlength{\parskip}{2pt} % Space between paragraphs

\begin{document}

%----------------------%
%     HEADER
%----------------------%
\begin{center}
    {\Huge \textbf{Sums Uz Zaman}}\\[3pt]
    Manhattan, New York \;\symbol{124}\; 978-942-8150 \;\symbol{124}\; \href{mailto:s.u.zaman@ieee.org}{s.u.zaman@ieee.org} \;\symbol{124}\; \href{https://linkedin.com/in/suzaman}{linkedin.com/in/suzaman}
\end{center}

%----------------------%
%     SUMMARY
%----------------------%
\vspace{1em}
\section*{Professional Summary}
Dynamic Cybersecurity professional with expertise in threat intelligence, incident response, and vulnerability management. Demonstrates proficiency in advanced malware analysis and cloud security, backed by multiple CompTIA certifications (Security+, Network+, and CySA+). Adept at applying security frameworks, automation, and emerging technologies to defend critical infrastructure. Eager to leverage strong communication and problem-solving skills to enhance organizational security posture in fast-paced environments.
\textbf{Authorized to work in the U.S. without sponsorship.}

%----------------------%
%   TECHNICAL SKILLS
%----------------------%
\section*{Technical Skills}
\begin{itemize}
    \item \textbf{Cybersecurity Tools \& Methodologies:} Splunk, Metasploit, Wireshark, Nessus, Burp Suite, Reverse Engineering (IDA/Ghidra)
    \item \textbf{Infrastructure \& Networking:} Firewalls (Cisco, Fortinet), VPNs, IDS/IPS, VLAN, TCP/IP, NAT
    \item \textbf{System Administration:} Windows Server (Active Directory, Group Policy), Linux (Kali, Ubuntu), VMware, Hyper-V
    \item \textbf{Scripting \& Automation:} Python (automation, ML), Bash, PowerShell, Git, GitHub (CI/CD)
    \item \textbf{Cloud Security:} AWS, Azure, GCP (IAM, data protection, threat intelligence)
    \item \textbf{EDR \& SIEM:} CrowdStrike, Carbon Black, Splunk ES, QRadar
    \item \textbf{Identity \& Access Management:} Okta, Azure AD, MFA, Role-based Access Control
    \item \textbf{Regulatory \& Compliance:} NIST, HIPAA, GDPR, SOAR Implementation
    \item \textbf{Blockchain \& IoT:} Solidity (private Ethereum networks), Raspberry Pi, Arduino
\end{itemize}

%----------------------%
%    CERTIFICATIONS
%----------------------%
\section*{Certifications}
\begin{itemize}
    \item CompTIA Security+
    \item CompTIA Network+
    \item CompTIA Cybersecurity Analyst (CySA+)
    \item Google Professional Cybersecurity Certificate
    \item Additional Training: AI Model Design with Python, Data Analytics
\end{itemize}

%----------------------%
%    EXPERIENCE
%----------------------%
\section*{Experience}
\textbf{Network \& Server Maintenance Specialist} \\
\textit{AK Consulting Services Inc., New York, NY} \hfill \textit{September 2024 -- Present}

\begin{itemize}
    \item Oversee and maintain routers, switches, firewalls, and VPNs to optimize network performance and security.
    \item Administer Windows and Linux servers (AD, DNS, DHCP) for seamless operations.
    \item Implement security best practices, conduct vulnerability assessments, and deploy timely patches.
    \item Investigated \& resolved network incidents, reducing average downtime by 30\% improving service availability.
    \item Collaborate on cybersecurity policies, incident response planning, and penetration tests.
    \item Contribute to forensic analysis and recovery measures to ensure business continuity.
\end{itemize}

\textbf{IT Support Specialist / Cybersecurity Intern} \hfill \textit{(Previous Experience)}
\begin{itemize}
    \item Provided Tier 1 and 2 support for hardware, software, and network issues in a fast-paced environment.
    \item Managed incident ticketing systems (ServiceNow, Jira) and prioritized technical tasks.
    \item Assisted with virtualization (VMware, Hyper-V) and endpoint security (CrowdStrike, Symantec).
    \item Automated administrative tasks via Bash and PowerShell scripting.
\end{itemize}

%----------------------%
%    PROJECTS
%----------------------%
%----------------------%
%    PROJECTS
%----------------------%
\section*{Projects}
\begin{itemize}
    \item \textbf{AI-Based Intrusion Detection System (2024):}
        Designed and implemented an AI-powered IDS using Python, TensorFlow, and network simulation tools, significantly boosting real-time threat detection accuracy. Tailored for IoT and self-driving car systems, enabling the early detection of zero-day attacks.

    \item \textbf{Malware Reverse Engineering (2024):}
        Analyzed advanced malware samples (Operation Triangulation/Pegasus, DoublePulsar) in a sandboxed environment. Examined assembly code, runtime behavior, and network activity to develop mitigation strategies. Documented findings and recommended countermeasures.

    \item \textbf{Wireless Security Survey (2023):}
        Executed vulnerability assessments on private Wi-Fi networks using Aircrack-ng and Wireshark. Identified security weaknesses and implemented enhancements to mitigate risks, improving overall network resilience.

    \item \textbf{Web App Incident Response (2023):}
        Contributed to a red team/blue team exercise focused on cloud security and IAM. Investigated misconfigurations and cyber-attacks in cloud environments, leveraging cloud-native and third-party tools. Demonstrated effective incident response in a simulated real-world scenario.

    \item \textbf{Private Blockchain Project (2022):}
        Developed a scalable private Ethereum blockchain using Solidity, Truffle, and VirtualBox. Demonstrated robust smart contract deployment and efficient handling of increased transactional loads, underscoring blockchain security principles.

    \item \textbf{Bluetooth Low Energy (BLE) Sniffer Device (2022):}
        Designed a BLE sniffer with an nRF51822 SoC and Wireshark for packet analysis. Captured BLE communications from nearby devices and logged results for further examination. Implemented a user-friendly GUI using Qt.

    \item \textbf{MMWave Radar Development (2022):}
        Created firmware and APIs for a 77\,GHz radar sensor using the NXP S32R2XX 32-bit processor. Optimized sensor data processing and user interface design, improving detection accuracy in advanced sensor applications.

    \item \textbf{TrashNet Object Detection (2022):}
        Built a real-time object detection system for recyclables using Python, OpenCV, and machine learning. Achieved over 90\% classification accuracy, enabling automated identification of recyclable items in various environments.
\end{itemize}


%----------------------%
%    EDUCATION
%----------------------%
\section*{Education}
\begin{itemize}
    \item \textbf{M.S. in Cybersecurity} \\[3pt]
          The City College of New York, \textit{May 2024}
    \item \textbf{B.Sc. in Electrical \& Electronic Engineering} \\[3pt]
          Bangladesh University of Engineering \& Technology, \textit{2018}
\end{itemize}
%----------------------%
%  AFFILIATIONS & LEADERSHIP
%----------------------%
\section*{Affiliations \& Leadership}
\begin{itemize}
    \item Assistant General Secretary, BUET Robotics Society (2016)
    \item Treasurer, IEEE BUET Student Branch (2016--2017)
    \item Organizing Secretary, BUET Robotics Society (2017)
    \item Student Activity Coordinator, IEEE Robotics \& Automation Society (RAS) - Bangladesh (2018--2019)
    \item Paper Reviewer, ICDCS 2019, PerCom 2020
\end{itemize}

%----------------------%
%   HONORS & AWARDS
%----------------------%
\section*{Honors \& Awards}
\begin{itemize}
    \item 1st Place -- International Autonomous Robotics Challenge (iARC), 2015
    \item Honorable Mention -- IEEE Signal Processing Cup, 2017
    \item 4th Place -- International Robotics Challenge (iRC), 2015
    \item National Finalist (Top 4) -- Microsoft Imagine Cup Bangladesh, 2016
\end{itemize}

%----------------------%
%    LANGUAGES
%----------------------%
\section*{Languages}
English (Fluent) \; | \; Bengali (Fluent) \; | \; Japanese (Intermediate)

%----------------------%
%   REFERENCES
%----------------------%
\section*{References}
Available upon request.

\end{document}
